\documentclass{class/llncs}
\usepackage[margin=1.3in]{geometry}
% \addtolength{\topmargin}{-.2in}
% \addtolength{\topmargin}{-.2in}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{color}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmicx}
% \usepackage{algorithm2e}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{comment}
\usepackage{mathrsfs} 
\usepackage{subcaption}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{array}
\usepackage{mathrsfs} 
\usepackage{booktabs}

\newtheorem{Theorem}{Theorem}
\newtheorem{Definition}{Definition}
\newtheorem{Observation}{Observation}


\title{Identity-Based Key Aggregate Cryptosystem from Multilinear Maps}
\begin{document}
% 
% \author{}
% \institute{}

\author{Sikhar Patranabis and Debdeep Mukhopadhyay}
\institute{Department of Computer Science and Engineering\\ Indian Institute of Technology Kharagpur
\\\{sikhar.patranabis, debdeep\}@cse.iitkgp.ernet.in}
\maketitle
\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}


\begin{abstract}

Secure online data sharing is one of the most important applications in today's world with far reaching impact in various fields. The advent of cloud computing has led to a massive requirement for secure, efficient, flexible and scalable data sharing schemes. A recent proposition in this regard is the \emph{key-aggregate cryptosystem}~(KAC). The main novelty of KAC is that it produces low overhead ciphertexts, and a low overhead decryption key that can aggregate the decryption rights to any arbitrarily large number of data classes. In this paper, we propose the first identity-based KAC where each data class can be associated with an unique identity. We present three different low-overhead KAC constructions based on $O(\log N)$-way multilinear maps that support $N$ different data classes using polylogarithmic size public and private parameters. The constructions are proven to be secure under different security guarantees and are fully collusion-resistant against any number of colluding parties. We present some real-world applications where identity-based KAC proves to be a viable and efficient solution.    

\noindent{\textbf{Keywords:}} Identity-based Key-Aggregate Cryptoystem, Online Data Sharing, Multilinear Maps, Collusion-resistant
\end{abstract}

\input{Source_Crypto/Introduction}
\input{Source_Crypto/Prelims}
\input{Source_Crypto/Proposal1}
\input{Source_Crypto/Proposal2}
\input{Source_Crypto/Applications}
\input{Source_Crypto/Proposal3}
\input{Source_Crypto/Conclusions}

% \begin{scriptsize}
\bibliographystyle{alpha}
\bibliography{bib/KeyAggregate}
% \end{scriptsize}

\newpage
\input{Source_Crypto/Appendix.tex}

\end{document}
